%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{DAVID} \headerlastnamestyle{SAFANYUK} \\
	\vspace{2mm}
	{\faEnvelope\ Dave.safanyuk@gmail.com} | {\faMobile\ 2158919927} | {\faMapMarker\ Langhorne, PA} | {\faLink\ https://www.linkedin.com/in/david-safanyuk/}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BS in Computer Science \& Software Engineering}
	{Pensacola Christian College}
	{Pensacola Christian College}
	{Sept 2015 – June 2019}
	{}
\end{cventries}

\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Devops Intern}
	{Comcast Corporation}
	{Philadelphia, PA}
	{May 2018 – August 2018}
	{\begin{cvitems}
		\item {Participated as a team member in migration of legacy database to new database cluster}
		\item {Created a CI/CD pipeline using Concourse and Ansible to automate the creation of AWS AMIs}
		\item {Member of agile team responsible for automating host provisioning}
		\item {Not only documented but also refactored an existing NodeJS api, to follow a design-driven development process.}
		\item {Worked with other teams to determine requirements, then worked with my team to develop, test, integrate and launch our product.}
		\end{cvitems}}
	\cventry
	{Software Engineering Intern}
	{Comcast Corporation}
	{Philadelphia, PA}
	{May 2016 – August 2016}
	{\begin{cvitems}
		\item {Created an interface for Bluetooth connections for the Comcast cable boxes.}
		\item {Participated in an optional internship project to develop a way to track and reduce employees’ carbon footprint.}
		\item {Added functionality to an internal tool to remotely trigger updates for cable boxes nationwide.}
		\end{cvitems}}
	\cventry
	{Operations Manager}
	{iDryfire Inc.}
	{Philadelphia, PA}
	{Jan 2014 – Present}
	{\begin{cvitems}
		\item {Operated 2 e-commerce sites and 2 other selling channels.}
		\item {Integrated 4 selling channels into a centralized system.}
		\item {Managed national sales team and organized international trade shows.}
		\item {Lead small marketing and development team to design advertisements and create websites.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming Languages:  & {\skill{ Javascript, Python, C/C++}} \\
		Software \& Frameworks:  & {\skill{ Git, Ansible, Concourse (CI/CD), NodeJS, AWS, MySQL, PostgreSQL, MongoDB}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}


\ 
\end{document}
